### 2018-08-08 paper/spor.tex
explained why only scalar prediction

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item \(\avail_d\) is the node's probability of being online in the near future. It computation will be discussed in~\ref{ssec:device_availability}.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}. Its function is analogous to 
Tor's authoritative directory servers, but we need a decentralized system. 
We will treat \(\avail_d\) in \cref{sec:squad_overlay}.

>>>>

\((d, \pk_d, \avail_d)\gets \GetRandomNode\): We assume that there is an 
algorithm \(\GetRandomNode\) which returns a tuple \((d, \pk_d, \avail_d)\) of 
one uniformly randomly selected node, where.
\begin{itemize}
  \item \(d\) is the node's identifier (address);
  \item \(\pk_d\) is the node's public key;
  \item  \(\avail_d(t)\) is the node's probability of being online as a function of time. 
  Its computation will be discussed in~\ref{ssec:device_availability}.
\end{itemize}
The \(\GetRandomNode\) algorithm can be instantiated using \eg
Octopus~\cite{Octopus}. Its function is analogous to 
Tor's authoritative directory servers, but we need a decentralized system. 
We will treat \(\avail_d\) in \cref{sec:squad_overlay}.

### 2018-08-08 paper/squad-overlay-design.tex
explained why only scalar prediction

The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\SPOR), as will be shown in the next subsection~\ref{ssec:por}.

>>>>

The predictive nature of \name lies in the fact that each participating device publicly advertises its probability of being connected in the near future. 
This information is used when any node needs to create a Stateless Predictive Probabilistic Onion Route (\acs{SPOR}), as was shown in section~\ref{SPOR}.

In the following, we refer to the node's probability of a node $d$ being online as the scalar $\Pon_d$, because $\forall t, \Pon_d(t) = \Pon_d$.
The estimate that is made accounts for the next state of the user's behavior in discrete time, and thus approximates the availability of $d$ in the near future.
The prediction eventually becomes stale, but we count on the fact that stale descriptors are removed fast in most RPS solutions: 
as a device calls \GetRandomNode, it only gets fresh descriptors.
